Value Ordering, Discrepancies, and Restarts in Subgraph Solvers: \\ Some Half-Baked Mucking Around

### 2017-09-27 paper/paper.tex
More things

We could try to introduce tiebreaking mechanisms to further refine this heuristic. However, given
the extreme cost of making an incorrect branching choice early on in search, we believe it is more
fruitful to investigate alternatives to simple backtracking (depth-first) search. This paper
evaluates two such approaches: discrepancy search, and restarts.

@@

@@

?? Talk about how we're not dealing with a binary search tree, so we could either make it binary, or
count one discrepancy each time the degree changes, or count every ``against'' branch as being just
one discrepancy regardless. ?? Has anyone done a proper job of this?

@@

?? In \cref{figure:others} we show that our solver is the bestest.

@@

?? Stick in Glasgow2, Glasgow3, VF2, SND if we can get it to run on the larger set of instances,
maybe SAT just to have something to cite showing how bad SAT is at this.

@@

In \cref{figure:restarts} we show the effects of adding restarts to the algorithm. With restarts,
the random variable-ordering heuristic comfortably beats the tailored strategy without restarts. In
other words, although having a good variable-ordering heuristic is beneficial, introducing
randomness into the search is better, if it is done alongside a mechanism to avoid heavy commitment
to any particular random choice.  However, the biased heuristic together with restarts is better
still---that is, if we are introducing restarts, then it is better to add a small amount of
randomness to a tailored deterministic heuristic than it is to throw away the heuristic altogether.

>>>>

We could try to introduce tiebreaking mechanisms to further refine this heuristic. However, given
the extreme cost of making an incorrect branching choice early on in search, we believe it is more
fruitful to investigate alternatives to simple backtracking (depth-first) search. This paper
evaluates two such approaches: discrepancy search (which perform poorly), and restarts (which are
extremely beneficial). To make restarts work, we introduce a new value-ordering heuristic, which is
nearly the same as ``highest degree first'' except with small amounts of heavily biased randomness.
The effects of the changes we propose are shown in the top plot of \cref{figure:scatter}: we can
make a state-of-the-art algorithm's perform much better on a large number of satisfiable instances,
without substantially degrading its performance on unsatisfiable or the remaining satisfiable
instances.

@@

?? Notation: $\vertexset(G)$, $\neighbourhood_G(v)$, $\nds_G(v)$, $\preceq$, $\sim_G$, $G^{a,b}$, $\mapsto$.

@@

?? Talk about how we're not dealing with a binary search tree, so we could either make it binary, or
count one discrepancy each time the degree changes, or count every ``against'' branch as being just
one discrepancy regardless.

@@

?? In \cref{figure:others} we show that our solver is the bestest. For each algorithm, the $y$ value
gives the cumulative number of instances which (individually) can be solved in no more than $x$
milliseconds.  The vertical distance between two lines therefore shows how many more instances can
be solved by one solver than another, if every instance is run separately with the chosen $x$
timeout; the horizontal distance shows how many times longer the per-instance timeout would need to
be to allow the rightmost algorithm to succeed on $y$ out of the 14,621 instances (bearing in mind
that the two sets of $y$ instances solved by the two algorithms could be completely different).

@@

?? Add in Glasgow2, Glasgow3, SND if we can get it to run on the larger set of instances,
maybe SAT just to have something to cite showing how bad SAT is at this.

@@

In \cref{figure:restarts} we show the effects of adding restarts to the algorithm. With restarts,
the random value-ordering heuristic comfortably beats the tailored strategy without restarts. In
other words, although having a good variable-ordering heuristic is beneficial, introducing
randomness into the search is better, if it is done alongside a mechanism to avoid heavy commitment
to any particular random choice.  However, the biased heuristic together with restarts is better
still---that is, if we are introducing restarts, then it is better to add a small amount of
randomness to a tailored deterministic heuristic than it is to throw away the heuristic altogether.
